---
title: "MPG Predictor App"
author: "Leão Pereira"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

## Introduction

This is a simple Shiny app that predicts the fuel efficiency (MPG) of a car based on its weight.

---

## Application Functionality

- **Input:** Car weight (slider)
- **Output:** Predicted MPG
- **Dataset:** `mtcars`
- **Model:** Simple linear regression (MPG ~ Weight)

---
---
title: "Interactive Car Analysis - MPG Dataset"
author: "Leão Pereira"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

## 1. Introduction

This presentation explores car performance using the `mpg` dataset.  
We combine interactive charts and map-based visuals to better understand fuel efficiency trends.

---

## 2. Fuel Efficiency by Class

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(dplyr)
library(leaflet)
library(tibble)
library(tidyr)

data(mpg)

p <- ggplot(mpg, aes(x = class, y = hwy, fill = class)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Highway MPG by Car Class", y = "MPG (Highway)", x = "")

ggplotly(p)
```

---

## 3. Engine Displacement vs Fuel Efficiency

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot_ly(data = mpg,
        x = ~displ,
        y = ~hwy,
        type = "scatter",
        mode = "markers",
        color = ~class,
        text = ~paste("Model:", model)) %>%
  layout(title = "Displacement vs Highway MPG",
         xaxis = list(title = "Engine Displacement"),
         yaxis = list(title = "Highway MPG"))
```

---

## 4. Map of Manufacturers (Sample Locations)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
fake_locations <- mpg %>%
  distinct(manufacturer) %>%
  mutate(lat = runif(n(), min = 25, max = 55),
         lon = runif(n(), min = -120, max = -70))

leaflet(fake_locations) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addMarkers(~lon, ~lat, popup = ~manufacturer, label = ~manufacturer)
```

---

## 5. Conclusion

- SUV and pickup classes tend to have lower highway MPG.
- Engine displacement is inversely correlated with fuel economy.
- Visual tools enhance exploration of performance patterns.
- Mapping manufacturers can support strategic decisions.

Thank you!

## The Model

```{r}
library(dplyr)
model <- lm(mpg ~ wt, data = mtcars)
summary(model)
```
